Identifying regime transitions for water governance: Take the Yellow River Basin in China as case

### 2023-05-12 paper/main/04_discussion.tex
docs(paper): :label: 更新了图3在讨论部分的引用

% 我们为的研究结果表明，黄河流域能被识别为三个明显的稳态。
In the case of the YRB, our results show that there have been three distinct governance regimes; we named them: a massive supply regime (P1: $1965 \sim 1978$), a governance transforming regime (P2: $1979 \sim 2001$), and an adaptation oriented regime (P3: $2002 \sim 2013$) (Figure~\ref{fig:IWGI}).
During the massive supply regime with lower water stress ($1965 \sim 1978$ in the YRB), water governance thus tended to boost water supply for services (mainly provisioning purposes then -livestock and crops) by constructing reservoirs and channels.
As the Chinese slogan ``man will conquer nature'' suggested then, however, the enhancement of water supply did not align with irreversible changes in the human-water relationship; it drastically increased water demand with little consideration for ecological conservation~\cite{zhou2020}.
The rapid expansion of irrigated farmland and water diversion facilities in the same decade brought the overburdened YRB close to a critical point, where increasing supply to meet demand was impractical~\cite{loch2020}.
Use of over $80\%$ of the surface water since 1972 has led to frequent river depletion, causing additional ecological issues such as wetland shrinkage and declines in biodiversity~\cite{wang2019c}.
In addition, since water stress also limited the growing industrial economy, the existing modes of water governance led to a social-ecological crisis~\cite{wohlfart2016}.

The start of the governance transforming regime (P2: $1979 \sim 2001$) coincided with rising competition for water use after the ``reform and opening-up''.
% 正如理论预测的那样
The results from the YRB mirror those of the theoretical analysis: continuous increases in water demand when the basin's total supply is stable can follow substantial changes in governance regime and a rapid enhancement in overall social adaptive capacity~\cite{loch2020}.
% 作为制度转变的先行者
As a pioneer in shifting governing institutions, the YRB triggered institutional changes during this regime. These include, for example, slowing the growth of irrigated acreage; leading water-saving infrastructure; creation of China's first water quota scheme, and the creation of a preliminary cross-boundary water transfer plan~\cite{wang2019e,long2020,nickum2021}.
% 因此，1999年黄河的最后一次枯竭
Consequently, although water stress remained and increased (due to reducing streamflow and flexibility), the last depletion of the Yellow River in 1999 led to a climax in this transformation in water governance~\cite{wang2019e}.

The ensuing adaptation-oriented regime (P3: $2002 \sim 2013$) involved a significant societal shift in adapting to stable high water stress.
% 一个基本背景是，在用水量总体保持稳定的情况下，黄河流域的径流量已显著低于从前，这是该时期水资源压力重新上升的重要原因。
Partially because of changed climate~\cite{han2023,liu2020c}, the runoff of the YRB was significantly lower than before when the overall water uses remained stable, which was an important reason for the rise of water stress in this stage (Figure~\ref{fig:runoff} and Figure~\ref{fig:scarcity}).
Socio-economic trade-offs between water-dependent regions and sectors, however, played a more important role in this regime, so water governance had to achieve efficient water allocation while balancing different demands in the face of limited water supply~\cite{dalin2015,song2022}.
Widespread reconstruction of resources in different industries and regions led to calls for adaptation in water governance, using the urgent requirements of adjusting rigid quota shares from the previous regime as an example~\cite{wang2019e}.
Many national-level governance practices were proposed under the regime because the absence of such policies to support high-quality development became new a structural challenge for water governance~\cite{konar2019}.

>>>>

% 我们为的研究结果表明，黄河流域能被识别为三个明显的稳态。
In the case of the YRB, our results show that there have been three distinct governance regimes; we named them: a massive supply regime (P1: $1965 \sim 1978$), a governance transforming regime (P2: $1979 \sim 2001$), and an adaptation oriented regime (P3: $2002 \sim 2013$) (Figure~\ref{fig:IWGI}).
During the massive supply regime with lower water stress ($1965 \sim 1978$ in the YRB), water governance thus tended to boost water supply for services (mainly provisioning purposes then -livestock and crops) by constructing reservoirs and channels (Figure~\ref{fig:Causes}~B).
As the Chinese slogan ``human will conquer nature'' suggested then, however, the enhancement of water supply did not align with irreversible changes in the human-water relationship; it drastically increased water demand with little consideration for ecological conservation~\cite{zhou2020}.
The rapid expansion of irrigated farmland and water diversion facilities in the same decade brought the overburdened YRB close to a critical point (Figure~\ref{fig:Causes}), where increasing supply to meet demand was impractical~\cite{loch2020}.
Use of over $80\%$ of the surface water since 1972 has led to frequent river depletion, causing additional ecological issues such as wetland shrinkage and declines in biodiversity~\cite{wang2019c}.
In addition, since water stress also limited the growing industrial economy, the existing modes of water governance led to a social-ecological crisis~\cite{wohlfart2016}.

The start of the governance transforming regime (P2: $1979 \sim 2001$) coincided with rising competition for water use after the ``reform and opening-up'' (Figure~\ref{fig:Causes}~C).
% 正如理论预测的那样
The results from the YRB mirror those of the theoretical analysis: continuous increases in water demand when the basin's total supply is stable can follow substantial changes in governance regime and a rapid enhancement in overall social adaptive capacity~\cite{loch2020}.
% 作为制度转变的先行者
As a pioneer in shifting governing institutions, the YRB triggered institutional changes during this regime. These include, for example, slowing the growth of irrigated acreage and leading water-saving infrastructure (Figure~\ref{fig:Causes}); creation of China's first water quota scheme, and the creation of a preliminary cross-boundary water transfer plan~\cite{wang2019e,long2020,nickum2021}.
% 因此，1999年黄河的最后一次枯竭
Consequently, although water stress remained and increased (due to reducing streamflow and flexibility), the last depletion of the Yellow River in 1999 led to a climax in this transformation in water governance~\cite{wang2019e}.

The ensuing adaptation-oriented regime (P3: $2002 \sim 2013$) involved a significant societal shift in adapting to stable high water stress.
% 一个基本背景是，在用水量总体保持稳定的情况下，黄河流域的径流量已显著低于从前，这是该时期水资源压力重新上升的重要原因。
Partially because of changed climate~\cite{han2023,liu2020c}, the runoff of the YRB was significantly lower than before when the overall water uses remained stable, which was an important reason for the rise of water stress in this stage (Supplementary Materials Figure~\ref{fig:runoff} and Figure~\ref{fig:scarcity}).
Socio-economic trade-offs between water-dependent regions and sectors, however, played a more important role in this regime, so water governance had to achieve efficient water allocation while balancing different demands in the face of limited water supply~\cite{dalin2015,song2022}.
Widespread reconstruction of resources in different industries and regions led to calls for adaptation in water governance, using the urgent requirements of adjusting rigid quota shares from the previous regime as an example~\cite{wang2019e}.
Many national-level governance practices were proposed under the regime because the absence of such policies to support high-quality development became new a structural challenge for water governance~\cite{konar2019}.

### 2023-05-12 paper/response_letter/source/reviewer_2.tex
feat(paper): :sparkles: 完成审稿人1的第一个意见修改
% 气候变化的确会产生很多影响，例如改变降水量和蒸发量。但这些影响都会以影响可用水量的形式体现在IWGI之中。 % 在新增加的图表中，我增加了天然水量的图表展示这种变化 % 例如气候变化让可用水量发生改变（scarcity），极端气候让我们难以有效的分配水资源（allocation），对气候变化的适应可能导致社会变革，让人们对愈发侧重于工业和经济发展的治理策略进行反思（priority）。 % 我们现在在讨论中涉及了这些话题。

Climate change is not explicitly represented in the index, which might play a key role in the streamflow recovery in the Yellow River in this century. Climate change would be a great challenge in the basin in the future. Significant climate change may affect the adaptive capacity of a basin and thus require different governance strategies.
do

@@

@@

@@

>>>>

\section{Reviewer \#2}\label{reviewer_2}

@@

\AR{} Thanks for the comment. We now improved the figure in the revised manuscript. % TODO 修改图1让它更清楚

@@

\AR{} Thanks for the suggestion. We now append refers in discussion when figure 3 is supporting:

\begin{quote}
    During the massive supply regime with lower water stress ($1965 \sim 1978$ in the YRB), water governance thus tended to boost water supply for services (mainly provisioning purposes then -livestock and crops) by constructing reservoirs and channels (Figure~\ref{fig:Causes}~B).
\end{quote}

\begin{quote}
    The rapid expansion of irrigated farmland and water diversion facilities in the same decade brought the overburdened YRB close to a critical point (Figure~\ref{fig:Causes}), where increasing supply to meet demand was impractical~\cite{loch2020}.
\end{quote}

\begin{quote}
    The start of the governance transforming regime (P2: $1979 \sim 2001$) coincided with rising competition for water use after the ``reform and opening-up'' (Figure~\ref{fig:Causes}~C).
\end{quote}

\begin{quote}
    As a pioneer in shifting governing institutions, the YRB triggered institutional changes during this regime. These include, for example, slowing the growth of irrigated acreage and leading water-saving infrastructure (Figure~\ref{fig:Causes});
\end{quote}

@@

% 感谢如此有趣的评论，虽然制度在特定的点发生变化，但我们认为总体来说是。这就像复杂系统中不是单独的一个，
\AR{} A good comment.
